MS_CNuptake.Rmd

### 2022-07-12 MS_CNuptake.Rmd
added comments regarding hard-coded numbers

# Setup 
```{r setup, include=FALSE}
rm(list=ls())
library(MLmetrics)
library(vhs)
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
#remotes::install_github("cj-holmes/vhs")
devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/")
library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

NPP_grassland$grassland_pred_anpp <- NPP_grassland$grassland_pred_npp * 0.49
NPP_grassland$grassland_pred_lnf <- NPP_grassland$grassland_pred_anpp/18
NPP_grassland$grassland_pred_bnpp <- NPP_grassland$grassland_pred_npp - NPP_grassland$grassland_pred_anpp
NPP_grassland$grassland_pred_bnf <- NPP_grassland$grassland_pred_bnpp/41
NPP_grassland$grassland_pred_nuptake <- NPP_grassland$grassland_pred_lnf*(1-0.69)+NPP_grassland$grassland_pred_bnf

@@

@@

>>>>

# Setup 
```{r setup, include=FALSE}
library(MLmetrics)
library(vhs) # remotes::install_github("cj-holmes/vhs")
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
#remotes::install_github("cj-holmes/vhs")
# devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/")
library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

# XXX what are these numbers (0.49, 18, 41, ...)?
NPP_grassland$grassland_pred_anpp <- NPP_grassland$grassland_pred_npp * 0.49
NPP_grassland$grassland_pred_lnf <- NPP_grassland$grassland_pred_anpp/18
NPP_grassland$grassland_pred_bnpp <- NPP_grassland$grassland_pred_npp - NPP_grassland$grassland_pred_anpp
NPP_grassland$grassland_pred_bnf <- NPP_grassland$grassland_pred_bnpp/41
NPP_grassland$grassland_pred_nuptake <- NPP_grassland$grassland_pred_lnf*(1-0.69)+NPP_grassland$grassland_pred_bnf

@@

# XXX what are these numbers (0.49, 1/18, 0.69, ...)?

@@

# XXX what are these numbers (0.49, 0.51, ...)?
